% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12

\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{xcolor}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encodings may result in incorrect characters.

\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.

% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}

\begin{document}

\title{Edge Computing in Cloud Computing}

%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here

\author{Galiléa LE MOULLEC (Mun ID: 202415993) \and Syed Aaquil Abbas (Mun ID: 202388362) \and Félicien MOQUET (Mun ID: 202415994)}


\authorrunning{G. Le Moullec, S.A. Abbas, F. Moquet}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.

\institute{Memorial University of Newfoundland, St. John's, Canada\\
\email{glemoullec@mun.ca}, \email{saabbas@mun.ca}, \email{fmoquet@mun.ca}}

\maketitle              % typeset the header of the contribution


\section*{}

\textbf{This document presents a preliminary and non-definitive outline of the topics we plan to address in our upcoming survey on Edge Computing. It serves as a roadmap, highlighting the key concepts, advantages, challenges, and future trends that will be explored in more depth in the final report.}

\section{Introduction}

Edge Computing is gaining prominence in the field of cloud computing due to its ability to process data closer to the end-users, reducing the dependency on centralized cloud resources and optimizing bandwidth usage. This section introduces the topic, its relevance, and the objectives of the study.

\subsection{Definition}
Definition and key characteristics of Edge Computing.

\subsection{Importance for Cloud Computing}
Why Edge Computing is essential in modern cloud infrastructures.

\subsection{Objectives of the Study}
Scope and goals of studying Edge Computing.

\section{Key Concepts of Edge Computing}
\subsection{Fundamental Principles}
\textcolor{blue}{Core principles and operational model.}

\subsection{Difference with Centralized Cloud Computing}
\textcolor{blue}{Comparing traditional cloud computing and Edge Computing.}

\subsection{Architecture and Key Components}
\textcolor{blue}{Overview of the architecture, including edge nodes and devices.}

\section{Advantages and Challenges}
\subsection{Advantages}

\begin{enumerate}
    \item \textcolor{blue}{Latency Reduction: Faster data processing and response times.}
    \item \textcolor{blue}{Bandwidth Optimization: Efficient bandwidth usage by processing data locally.}
    \item Enhanced Security and Privacy: Enhancing security and privacy by reducing data transfers.
    \item Decentralized Data Processing: Distributed computing model reducing cloud dependency.
\end{enumerate}

\subsection{Challenges}
\begin{enumerate}
    \item \textcolor{blue}{Managing Distributed Resources: Handling computing resources across different edge nodes.}
    \item \textcolor{blue}{Security and Regulatory Compliance: Addressing regulatory and security challenges.}
    \item Interoperability with Cloud Computing: Ensuring seamless integration with existing cloud infrastructure.
    \item Cost and Maintenance of Edge Infrastructures: Evaluating the financial and operational implications.
\end{enumerate}

\section{Applications and Use Cases}
\subsection{Internet of Things (IoT)}
\textcolor{blue}{Role of Edge Computing in IoT networks.}

\subsection{Autonomous Vehicles}
Application of Edge Computing in self-driving vehicles.

\subsection{Smart Cities and Intelligent Infrastructure}
Enhancing urban management with edge-based technologies.

\subsection{Industry and Manufacturing}
\textcolor{blue}{Industrial automation and real-time analytics.}

\subsection{Healthcare and Telemedicine}
Role of Edge Computing in healthcare and remote diagnostics.

\section{Trends and Future Perspectives}
\subsection{Technological Evolution and Innovation}
\textcolor{blue}{Advancements and innovations in Edge Computing.}

\subsection{Integration with Artificial Intelligence and 5G}
How AI and 5G enhance Edge Computing.

\subsection{Research Challenges and Future Developments}
\textcolor{blue}{Current challenges and future directions in research.}

\section{Conclusion}
\subsection{Importance of Edge Computing in the Evolution of Cloud Computing}
Summary of the role of Edge Computing in modern infrastructures.

\subsection{Growth and Research Perspectives}
Future research opportunities and expected advancements.

\end{document}
